Avoiding the Global Sort: \break A Faster Contour Tree Algorithm

### 2017-05-03 paint-contour-tree.tex
figure added

\usepackage{amsfonts,amsmath,amssymb,amsthm,mathtools}
\usepackage{paralist}
\usepackage{algorithmic,algorithm}
\usepackage{bm}
\usepackage{xspace}
\usepackage{centernot}
\usepackage{fancybox}
\usepackage{framed}
\usepackage{xspace}
\usepackage{prettyref}
%\usepackage[dvipsnames,usenames]{color}
\usepackage{caption}
\usepackage{color}
\usepackage{graphics}
%\usepackage[pagebackref,colorlinks=true,urlcolor=blue,linkcolor=blue,citecolor=BrickRed,pdfstartview=FitH]{hyperref}
\usepackage{hyperref}%
\hypersetup{%
   breaklinks,%
   colorlinks=true,%
   urlcolor=[rgb]{0.2,0.0,0.0},
   linkcolor=[rgb]{0.5,0.0,0.0},%
   citecolor=[rgb]{0,0,0.445},
   filecolor=[rgb]{0,0,0.4},
   anchorcolor=[rgb]{0.0,0.1,0.2}
}

@@

>>>>

\usepackage{subcaption}
\usepackage{amsfonts,amsmath,amssymb,amsthm,mathtools}
\usepackage{paralist}
\usepackage{algorithmic,algorithm}
\usepackage{bm}
\usepackage{xspace}
\usepackage{centernot}
\usepackage{fancybox}
\usepackage{framed}
\usepackage{xspace}
\usepackage{prettyref}
%\usepackage[dvipsnames,usenames]{color}
\usepackage{caption}
\usepackage{color}
\usepackage{graphics}
%\usepackage[pagebackref,colorlinks=true,urlcolor=blue,linkcolor=blue,citecolor=BrickRed,pdfstartview=FitH]{hyperref}
\usepackage{hyperref}%
\hypersetup{%
   breaklinks,%
   colorlinks=true,%
   urlcolor=[rgb]{0.2,0.0,0.0},
   linkcolor=[rgb]{0.5,0.0,0.0},%
   citecolor=[rgb]{0,0,0.445},
   filecolor=[rgb]{0,0,0.4},
   anchorcolor=[rgb]{0.0,0.1,0.2}
}

@@

\pagebreak
\appendix

\section{ \Sec{algo} Algorithm Example }

\textcolor{red}{
In the example below, I assumed that the maxima are already considered ``processed'', so that there are not additional trivial steps.  
This actually makes more sense since the $att()$ should really only ever point to already processed vertex.  Therefore, I suggest 
changing line 3 of init to ``Mark all maxima as processed.  Mark all other critical $v$ as unprocessed.''
Perhaps line 4 needs to be changed also?
}

 \begin{figure}[h]\centering
    \includegraphics[width=.3\linewidth,page=1]{figs/mesh1}
    \caption{A piece of a potentially larger mesh, with maxima $m_1,m_2,m_3$, saddles $s_1,s_2$, and regular vertices $r_1,r_2,r_3,r_4$.
             An initial painting is shown where green `g' is spilled from $m_1$, then red `r' from $m_2$, and finally blue `b' from $m_3$.
             Arrows are directed from higher to lower function value.}
    \label{fig:mesh1}
\end{figure} 
%
\begin{figure}[h]
   \begin{subfigure}{.33\textwidth}
     \centering
     \includegraphics[width=.7\linewidth,page=1]{figs/mesh2}
     \caption{}
     \label{fig:tree1}
   \end{subfigure}%
   \begin{subfigure}{.33\textwidth}
     \centering
     \includegraphics[width=.7\linewidth,page=2]{figs/mesh2}
     \caption{}
     \label{fig:tree2}
   \end{subfigure}
   \begin{subfigure}{.33\textwidth}
     \centering
     \includegraphics[width=.7\linewidth,page=3]{figs/mesh2}
     \caption{}
     \label{fig:tree3}
   \end{subfigure}
 \caption{Snapshots of the join tree.}
 \label{fig:mesh2}
\end{figure}
%
\begin{figure*}[h]%
    \centerline{%
       \begin{tabular}{|l|c|c|c|c|c|c|c|c|}%
         \hline
         Stage%
         &%
           $att(r)$
         &%
           $att(g)$
         &%
           $att(b)$
         &%
           $T(r)$
         &%
           $T(g)$
         &%
           $T(b)$
         &%
           $K$
         &%
          Current tree\\
         \hline%
         \hline%
         Initial
         &%
           $m_2$
         &%
           $m_1$
         &%
           $m_3$
         &%
           $\{s_2\}$
         &%
           $\{s_1\}$
         &%
           $\{s_1,s_2\}$
         &%
           $()$
         &%
           \Fig{tree1}
         \\%
         \hline%
         % 
         1%
         &%
           $m_2$          
         &%
           $m_1$
         &%
           $m_3$
         &%
           $\{s_2\}$
         &%
           $\{s_1\}$
         &%
           $\{s_1,s_2\}$
         &%
           $(s_1)$
         &%
           \Fig{tree1}
         \\%
         \hline%
         %
         2
         &%
           $m_2$
         &%
           $m_1$
         &%
           $m_3$
         &%
           $\{s_2\}$
         &%
           $\{s_1\}$
         &%
           $\{s_1,s_2\}$
         &%
           $(s_1,s_2)$
         &%
           \Fig{tree1}
         \\%
         \hline%
         %
         3
         &%
           NA
         &%
           $m_1$
         &%
           $s_2$
         &%
           NA
         &%
           $\{s_1\}$
         &%
           $\{s_1\}$
         &%
           $(s_1)$
         &%
           \Fig{tree2}
         \\%
         \hline%
         %
         4
         &%
           NA
         &%
           NA
         &%
           $s_1$
         &%
           NA
         &%
           NA
         &%
           $\{\}$
         &%
           $()$
         &%
           \Fig{tree3}
         \\%
         \hline
       \end{tabular}%
    }
    \caption{Stages of the algorithm run on the initial painting shown in \Fig{mesh1}.
    The above table assumes that in the stack update, $s_1$ is the first arbitrary unprocessed critical point selected.}
    \label{fig:exec}
\end{figure*}
